---
title: "workout03-report"
author: "Cora Bai"
date: "11/26/2018"
output: github_document
---
```{r}
library("roller")
```
##Getting Started with rolling an object
Object Rolling
The package "roller" is a minimalistic simulation of rolling an object with different sides and probability a given number of times, and to visualize the relative frequencies in graphs.

###Creating a device
The first step is to create a "device" object with the function device():

```{r}
defaultdevice <- device()
defaultdevice
```

By default, device() creates a fair device with standard sides 1, representing head and 2, representing tail and with probability values for each side of 0.5. This object is similiar to a coin.

Now we can change the parameters from default to sides and prob: make sure the sides and probability satisfy the respective requirements (ie: length sides should be larger than 1)

```{r}
loaded <- device(sides = c(1, 2), prob = c(0.8, 0.2))
loaded
```


###Rolling a device
Once you have defined a "device" object, you can use the function roll() to roll the device a given number of times. The output will be an object of class "rolls"

```{r}
roll100 <- roll(defaultdevice, times = 100)
roll100
```

The summary.rolls() function gives you a table of frequencies:

```{r}
summary(roll100)
```

###Plot of relative frequencies
You can use the function plot() to create a graphic with the relative frequencies of a series of rolling devices:

```
plot(roll100)
```